Generating Simulated Data

### 2021-03-25 docs/SimData.Rmd
age length pairs continued

# VBGF packages all take age and length pairs, reformat from length comp at agecl

#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenage <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%

>>>>

# need to shift agecl to represent midpoint of actual age groups
# using part of the wtage interpolation function calc_avgwtstage2age()
annage_comp_data <- read_savedsurvs(d.name, 'survAnnAge')

library(FSA)
# VBGF packages all take age and length pairs, reformat from length comp at agecl
# break into 3 chunks of time, "era" 48 years each more like our survey
# subsample after reformatting with uncount because we wouldn't have this many ages

#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){

  annages <- annage_comp_data[[s]][[1]] %>%
    group_by(species, time, agecl) %>%
    rename(trueage = agecl) %>%
    summarise(truenatage = sum(atoutput))

  # Figure out the groups that have multiple ages classes in each stage (or
  # cohort)
  multiple_ages <- sp_age[sp_age$NumAgeClassSize>1,]

  # finds the average age of each agecl each timestep based on truenatage
  svlen_avgage <- annages %>%
    dplyr::semi_join(len_comp_data[[s]][[1]], by = c("species", "time")) %>%
    dplyr::inner_join(multiple_ages, by = c("species" = "Name")) %>%
    dplyr::mutate(agecl = as.integer(ceiling(trueage/NumAgeClassSize))) %>%
    dplyr::group_by(species, time, agecl) %>%
    dplyr::mutate(avgage = weighted.mean(trueage, truenatage))

  #arrange into long format: year, Species, agecl, length 
  svlenage <- len_comp_data[[s]][[1]] %>%
    dplyr::left_join(svlen_avgage) %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, avgage, year, upper.bins, atoutput) %>%
    dplyr::mutate(avgage = coalesce(avgage,agecl)) %>%
    dplyr::rename(length = upper.bins) %>%
    dplyr::mutate(era = as.numeric(cut_number(year,3))) %>%
    tidyr::uncount(atoutput) %>%
    dplyr::group_by(species, avgage, year) %>%
    dplyr::sample_frac(0.01)

  svvbgf <- svlenage %>%
    dplyr::group_by(species, era) %>%
    group_map(~nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .)))
